### 2015-10-17 locking.tex
restructure for sync with Authorea
try another way
integrate to author
force pdflatex to pick up the .pdf files (picks .png otherwise)
don't say unbounded, and don't speculate what happens for arbitrary deadlines D_i > T_i

\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{../figures/locking/legend}
  \includegraphics[scale=1]{../figures/locking/sched-locking-alt1}
  \caption{Example schedule of two tasks $\tau_1$ and $\tau_2$ on two processors sharing one lock-protected resource. The example assumes that lock requests take effect only when the critical section segment  becomes eligible to be scheduled according to the rules of the period enforcer algorithm. Under this interpretation, the fourth job of task $\tau_2$ misses its deadline at time $28$.}
  \label{fig:locking-alt1}
  \end{figure}

@@

\subsection{Case 2: Locking Takes Effect Immediately}
 From now on, we assume the second interpretation: all lock requests are processed immediately when they are made, even if this causes the shared resource to be locked by a task that is not yet eligible to execute according to  the rules of the period enforcer algorithm. We construct an example that demonstrates \emph{unbounded} response-time growth.

@@

The third jobs of both tasks are released at time $16$. The roles are swapped again: because $\tau_2$'s first segment requires only $1-\epsilon$ time units of service, it acquires the lock at time $a^2_{2,3} = 17 - \epsilon$, before $\tau_1$ issues its request at time~$17$. However, according to the period enforcer algorithm's eligibility criterium, $\tau_2$ cannot actually continue its execution before time $21- \epsilon$ since
\begin{align*}
	ET_{2,3}^2 & = \max\left(ET_{2,2}^2 + T_2,\ \mathit{busy}(\tau_2, a^2_{2,3})\right) =\max(13- \epsilon + 8,\ 16) = 21- \epsilon.
\end{align*}
This, however, means that $\tau_1$ cannot use the shared resource before time $23 - \epsilon$, which leaves insufficient time to complete the second segment of $\tau_1$'s third job before its deadline at time $24$.
Furthermore, if both tasks continue the illustrated execution pattern, the period enforcer continues to increase their response times. As a result,  unbounded worst-case response times may arise.

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{../figures/locking/legend}
  \includegraphics[scale=1]{../figures/locking/sched-locking-alt2}
  \caption{Example schedule of two tasks $\tau_1$ and $\tau_2$ on two processors sharing one lock-protected resource. The example assumes that lock requests take effect immediately, even if the critical section segment is not yet eligible to be scheduled according to the rules of the period enforcer algorithm. Under this interpretation, the third job of task $\tau_1$ misses its deadline at time $24$.}
  \label{fig:locking-alt2}
  \end{figure}

>>>>

\ifpaper
\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{../figures/locking/legend.pdf}
  \includegraphics[scale=1]{../figures/locking/sched-locking-alt1.pdf}
  \caption{Example schedule of two tasks $\tau_1$ and $\tau_2$ on two processors sharing one lock-protected resource. The example assumes that lock requests take effect only when the critical section segment  becomes eligible to be scheduled according to the rules of the period enforcer algorithm. Under this interpretation, the fourth job of task $\tau_2$ misses its deadline at time $28$.}
  \label{fig:locking-alt1}
  \end{figure}
\fi

@@

\subsection{Case 2: Locking Takes Effect Immediately}
 From now on, we assume the second interpretation: all lock requests are processed immediately when they are made, even if this causes the shared resource to be locked by a task that is not yet eligible to execute according to  the rules of the period enforcer algorithm. We construct an example in which a task's response time grows with each job until a deadline is missed.

@@

The third jobs of both tasks are released at time $16$. The roles are swapped again: because $\tau_2$'s first segment requires only $1-\epsilon$ time units of service, it acquires the lock at time $a^2_{2,3} = 17 - \epsilon$, before $\tau_1$ issues its request at time~$17$. However, according to the period enforcer algorithm's eligibility criterium, $\tau_2$ cannot actually continue its execution before time $21- \epsilon$ since
\begin{align*}
	ET_{2,3}^2 & = \max\left(ET_{2,2}^2 + T_2,\ \mathit{busy}(\tau_2, a^2_{2,3})\right) =\max(13- \epsilon + 8,\ 16) = 21- \epsilon.
\end{align*}
This, however, means that $\tau_1$ cannot use the shared resource before time $23 - \epsilon$, which leaves insufficient time to complete the second segment of $\tau_1$'s third job before its deadline at time $24$.
Furthermore, if both tasks continue the illustrated execution pattern, the period enforcer continues to increase their response times. As a result, the pattern may be repeated to construct schedules in which an arbitrarily large implicit or constrained deadline is violated.

@@

\ifpaper
\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{../figures/locking/legend.pdf}
  \includegraphics[scale=1]{../figures/locking/sched-locking-alt2.pdf}
  \caption{Example schedule of two tasks $\tau_1$ and $\tau_2$ on two processors sharing one lock-protected resource. The example assumes that lock requests take effect immediately, even if the critical section segment is not yet eligible to be scheduled according to the rules of the period enforcer algorithm. Under this interpretation, the third job of task $\tau_1$ misses its deadline at time $24$.}
  \label{fig:locking-alt2}
  \end{figure}
\fi
